WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-06-10 lit/sec_2-lead.tex
Fixed: Bib IEEE style

\acrfull{lead} \cite{Droegemeier2005Service-OrientedWeather} addresses the fundamental research challenges needed to create an integrated and scalable framework for adaptive analysis and prediction of the atmosphere. The weather forecasting researchers require many computer resources to predict and analyze weather models in the mesoscale with less time. Rather than each researcher run and handle their computer resources for the weather experiments, LEAD provides a shared pool of resources. Then the researchers can use the resource pool to run their experiment in shorter amounts of time and a more massive scale. At the time, some researchers are developing their experiment forecasting flows, they are not using the resources, and other researchers can run their forecasting flows using available resources. The foundation of the LEAD system is to create a dynamic workflow orchestration and data management in a web services framework \cite{Droegemeier2005Service-OrientedWeather}.

LEAD's complex range of services, applications, interfaces, and IT resources, local and external networks, and storage is compiled by users in workflows to study mesoscale incremental manner \cite{Droegemeier2005Service-OrientedWeather}. As it follows the SOA, all the features are implemented as independent services. The above implementation enables LEAD to scale up each service as required and update each service without affecting other services. New models that are required for implementing a new forecast flow also have to be implemented as a service and then integrate into the system.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{lit/lead/LEAD-system-Fundamental-capabilities-familiar-to-meteorologists-are-shown-in-the-top_W640.png}
    \caption[Layered architecture of LEAD]{Layered architecture of LEAD \cite{Droegemeier2005Service-OrientedWeather}.}
    \label{fi:lead_system}
\end{figure}

The second layer contains fundamental tools such as the following to help to link services together \cite{Droegemeier2005Service-OrientedWeather}:
\begin{itemize}
    \item The users interact with LEAD via a web portal
    \item Data quality control and assimilation happens via ARPS Data Assimilation System (ADAS)
    \item myLEAD is the metadata catalog
    \item \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel}
    \item Algorithm development and mining is a set of tools for analyzing observational data, assimilated data sets, and model output
    \item Integrated data viewer 
\end{itemize}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{lit/lead/LEAD-system-framework-LEAD-is-composed-of-several-interacting-subsystems-with-the-LEAD_W640.png}
    \caption[LEAD system framework]{LEAD system framework \cite{Droegemeier2005Service-OrientedWeather}.}
    \label{fi:lead_framework}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{lit/lead/LEADs-service-oriented-architecture-A-wide-variety-of-services-and-resources-grouped_W640.png}
    \caption[LEAD's service-oriented architecture]{LEAD's service-oriented architecture \cite{Droegemeier2005Service-OrientedWeather}.}
    \label{fi:lead_soa}
\end{figure}

As shown in \cref{fi:lead_soa}, \acrshort{lead} \acrshort{soa} has five different but highly interconnected layers. The bottom layer represents the calculation, application, and raw data sources that are distributed in the LEAD grid and elsewhere. The next level supports web services that provide access to raw services \cite{Droegemeier2005Service-OrientedWeather}. These two layers are working together since LEAD system resources are distributed over multiple locations and creating a pool of resources. The upper layer of the raw resources is abstracting the complexity of managing and accessing the resources and provides simplified access. In the upper layers, the underline system is viewed as an unlimited resource pool for storing and handling data.

>>>>

\acrfull{lead} \cite{Droegemeier2005Service-orientedWeather} addresses the fundamental research challenges needed to create an integrated and scalable framework for adaptive analysis and prediction of the atmosphere. The weather forecasting researchers require many computer resources to predict and analyze weather models in the mesoscale with less time. Rather than each researcher run and handle their computer resources for the weather experiments, LEAD provides a shared pool of resources. Then the researchers can use the resource pool to run their experiment in shorter amounts of time and a more massive scale. At the time, some researchers are developing their experiment forecasting flows, they are not using the resources, and other researchers can run their forecasting flows using available resources. The foundation of the LEAD system is to create a dynamic workflow orchestration and data management in a web services framework \cite{Droegemeier2005Service-orientedWeather}.

LEAD's complex range of services, applications, interfaces, and IT resources, local and external networks, and storage is compiled by users in workflows to study mesoscale incremental manner \cite{Droegemeier2005Service-orientedWeather}. As it follows the SOA, all the features are implemented as independent services. The above implementation enables LEAD to scale up each service as required and update each service without affecting other services. New models that are required for implementing a new forecast flow also have to be implemented as a service and then integrate into the system.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{lit/lead/LEAD-system-Fundamental-capabilities-familiar-to-meteorologists-are-shown-in-the-top_W640.png}
    \caption[Layered architecture of LEAD]{Layered architecture of LEAD \cite{Droegemeier2005Service-orientedWeather}.}
    \label{fi:lead_system}
\end{figure}

The second layer contains fundamental tools such as the following to help to link services together \cite{Droegemeier2005Service-orientedWeather}:
\begin{itemize}
    \item The users interact with LEAD via a web portal
    \item Data quality control and assimilation happens via ARPS Data Assimilation System (ADAS)
    \item myLEAD is the metadata catalog
    \item \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel}
    \item Algorithm development and mining is a set of tools for analyzing observational data, assimilated data sets, and model output
    \item Integrated data viewer 
\end{itemize}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{lit/lead/LEAD-system-framework-LEAD-is-composed-of-several-interacting-subsystems-with-the-LEAD_W640.png}
    \caption[LEAD system framework]{LEAD system framework \cite{Droegemeier2005Service-orientedWeather}.}
    \label{fi:lead_framework}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{lit/lead/LEADs-service-oriented-architecture-A-wide-variety-of-services-and-resources-grouped_W640.png}
    \caption[LEAD's service-oriented architecture]{LEAD's service-oriented architecture \cite{Droegemeier2005Service-orientedWeather}.}
    \label{fi:lead_soa}
\end{figure}

As shown in \cref{fi:lead_soa}, \acrshort{lead} \acrshort{soa} has five different but highly interconnected layers. The bottom layer represents the calculation, application, and raw data sources that are distributed in the LEAD grid and elsewhere. The next level supports web services that provide access to raw services \cite{Droegemeier2005Service-orientedWeather}. These two layers are working together since LEAD system resources are distributed over multiple locations and creating a pool of resources. The upper layer of the raw resources is abstracting the complexity of managing and accessing the resources and provides simplified access. In the upper layers, the underline system is viewed as an unlimited resource pool for storing and handling data.

### 2020-06-10 method/sec_0_introduction.tex
Fixed: Bib IEEE style

To get an overall idea of the flow of weather forecast, let us look into one of the weather forecasting flows in the \acrshort{curw} \cite{CUrWSL2017SL}.

>>>>

To get an overall idea of the flow of weather forecast, let us look into one of the weather forecasting flows in the \acrshort{curw} \cite{CUrWSL2017Lanka}.

### 2020-06-10 method/sec_4-db_struct.tex
Caption .
Fixed: Bib IEEE style

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{method/microservice/wdias_database_structure.pdf}
    \caption{\acrshort{wdias} database structure}
    \label{fi:database_structure}
\end{figure}

@@

We used Redis \cite{redisRedisDocumentation} as the in-memory database since it is a widely used database system with excellent support. It also supports Publisher Subscriber capabilities as an inbuilt feature. Redis is an open-source tool, and clustering is also available for scalability. Redis uses in-memory caching for fast access to the frequent access data in adapter-metadata and adapter-extension. Other than that, status adapter uses Redis as a key-value pair store to maintain the status for asynchronous requests handling while storing grid data. The extension adapter uses Redis's Publisher Subscriber capabilities to create a cronjob in extension scheduler service when a new extension creates with a trigger on time during data preprocessing.

@@

Among several timeseries open source databases, InfluxDB \cite{influxdbInfluxDBDocumentation} uses a unique database indexing algorithm to gain higher performance while storing timeseries data when compared to other modern databases available. Also, it has better support, higher usage, and following supports,

@@

\acrshort{netCDF} \cite{unidataUnidataNetCDF} is a self-describing, machine-independent data format that supports the creation, access, and sharing of array-oriented scientific data. Moreover, NetCDF also supports parallel file access. NetCDF is widely used in the scientific domain due to the capability of storing multi-dimensions data efficiently and flexibly. Thus, we used NetCDF for storing the grid data due to its capability of storing array-oriented scientific data efficiently when compared to other database systems.

@@

To provide fast geo-search queries, we have to use a database system that supports geo indexing. We used MongoDB, which is a document-oriented database with geo indexing capabilities. Also, MongoDB \cite{mongodbMongoDBManual} is a general-purpose, document-based, distributed database, and supports,

\begin{itemize}
  \item Supports query operations on geospatial data \cite{mongodbMongoDBManual}
  \item Clustering and Sharding available for scalability and reliability
\end{itemize}

>>>>

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{method/microservice/wdias_database_structure.pdf}
    \caption{\acrshort{wdias} database structure.}
    \label{fi:database_structure}
\end{figure}

@@

We used Redis \cite{RedisRedisDocumentation} as the in-memory database since it is a widely used database system with excellent support. It also supports Publisher Subscriber capabilities as an inbuilt feature. Redis is an open-source tool, and clustering is also available for scalability. Redis uses in-memory caching for fast access to the frequent access data in adapter-metadata and adapter-extension. Other than that, status adapter uses Redis as a key-value pair store to maintain the status for asynchronous requests handling while storing grid data. The extension adapter uses Redis's Publisher Subscriber capabilities to create a cronjob in extension scheduler service when a new extension creates with a trigger on time during data preprocessing.

@@

Among several timeseries open source databases, InfluxDB \cite{InfluxDBInfluxDBDocumentation} uses a unique database indexing algorithm to gain higher performance while storing timeseries data when compared to other modern databases available. Also, it has better support, higher usage, and following supports,

@@

\acrshort{netCDF} \cite{UnidataNetworkForm} is a self-describing, machine-independent data format that supports the creation, access, and sharing of array-oriented scientific data. Moreover, NetCDF also supports parallel file access. NetCDF is widely used in the scientific domain due to the capability of storing multi-dimensions data efficiently and flexibly. Thus, we used NetCDF for storing the grid data due to its capability of storing array-oriented scientific data efficiently when compared to other database systems.

@@

To provide fast geo-search queries, we have to use a database system that supports geo indexing. We used MongoDB, which is a document-oriented database with geo indexing capabilities. Also, MongoDB \cite{MongoDBMongoDBManual} is a general-purpose, document-based, distributed database, and supports,

\begin{itemize}
  \item Supports query operations on geospatial data \cite{MongoDBMongoDBManual}
  \item Clustering and Sharding available for scalability and reliability
\end{itemize}

### 2020-06-10 results/sec_2-workload.tex
Caption .
Fixed: Bib IEEE style

We used 250 locations from Google’s countries public data set \cite{GoogleGoogleCounties}, and considered static throughout the testing. For each location, we created four timeseries metadata by using four different values for the moduleId key attribute. Thus, combining all together first, we created 1000 timeseries metadata during the performance test and then stored the timeseries data against timeseries unique identifiers. We have written automated scripts to generate these data for the performance testing, and scripts are generic enough to create more timeseries metadata by changing the configurations.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{results/work_load/experimental_setup_v3.pdf}
    \caption{Experimental setup with JMeter}
    \label{fi:experimental_setup}
\end{figure}

@@

While implementing the test cases for \acrshort{wdias}, we used the concurrency thread group with the throughput shaping timer extension of JMeter because it supports the open workload approach. Using other thread groups, we are required to find the exact number of threads and timer delays that produce the desired number of \acrshort{rps} to the server, which is known as the \emph{closed workload}. By using the \emph{throughput shaping timer}, we only need to configure the \acrshort{rps} throughout the test plan. Then the throughput shaping timer provides a feedback loop to the concurrency thread group via schedule feedback function to dynamically maintain thread count required to achieve target \acrshort{rps} \cite{KarunarathneGihanWdias/wdias-performance-test:JMeter.}.

@@

With the above JMeter test plans, we have to enable each test plan separately and before running with JMeter distributed mode. To make the process faster, we implemented a script tool to interact with the JMeter test stored files. The script is available within the code base \cite{KarunarathneWdias-performance-test/TEST_PLAN.md:Plan} as \emph{test-dev} and supports the following features.

@@

We have documented a detailed description of setting up the \acrshort{eks} \cite{KarunarathneWdias/Amazon_EKS.md:EKS}, and it is available in the codebase of the \acrshort{wdias}. \acrshort{k8s} is a planet scaling tool \cite{LinuxFoundationProduction-GradeKubernetes}, and users can tweak the configuration to run the \acrshort{wdias} as per the required level of load on the system. We used a set of physical nodes, as mentioned in \cref{tab:aws_eks_nodes}, to set up the \acrshort{k8s} for the performance testing with a peak of 300 \acrshort{rps}.

@@

The \acrshort{wdias} uses Helm \cite{CNCFHelmDocs} which is a package manager for \acrshort{k8s}. Each microservice within the system deploys and maintains as a Helm chart and the Helm charts \cite{KarunarathneWdias-helm-charts:Deployments} for each microservice available within the codebase. For the databases, we used the official helm charts. Using Helm, we can configure resources, the number of replicas needed, deploy new changes, and manage credentials, storage, and proxy settings that are needed for each microservice.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.75\textwidth]{results/work_load/eks_node_setup.pdf}
    \caption{\acrfull{eks} node setup}
    \label{fi:eks_node_setup}
\end{figure}

>>>>

We used 250 locations from Google’s countries public data set \cite{GoogleGoogleCountries}, and considered static throughout the testing. For each location, we created four timeseries metadata by using four different values for the moduleId key attribute. Thus, combining all together first, we created 1000 timeseries metadata during the performance test and then stored the timeseries data against timeseries unique identifiers. We have written automated scripts to generate these data for the performance testing, and scripts are generic enough to create more timeseries metadata by changing the configurations.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{results/work_load/experimental_setup_v3.pdf}
    \caption{Experimental setup with JMeter.}
    \label{fi:experimental_setup}
\end{figure}

@@

While implementing the test cases for \acrshort{wdias}, we used the concurrency thread group with the throughput shaping timer extension of JMeter because it supports the open workload approach. Using other thread groups, we are required to find the exact number of threads and timer delays that produce the desired number of \acrshort{rps} to the server, which is known as the \emph{closed workload}. By using the \emph{throughput shaping timer}, we only need to configure the \acrshort{rps} throughout the test plan. Then the throughput shaping timer provides a feedback loop to the concurrency thread group via schedule feedback function to dynamically maintain thread count required to achieve target \acrshort{rps} \cite{KarunarathneWDIASJMeter}.

@@

With the above JMeter test plans, we have to enable each test plan separately and before running with JMeter distributed mode. To make the process faster, we implemented a script tool to interact with the JMeter test stored files. The script is available within the code base \cite{KarunarathneWDIASPlan} as \emph{test-dev} and supports the following features.

@@

We have documented a detailed description of setting up the \acrshort{eks} \cite{KarunarathneWDIASService}, and it is available in the codebase of the \acrshort{wdias}. \acrshort{k8s} is a planet scaling tool \cite{LinuxFoundationKubernetes:Orchestration}, and users can tweak the configuration to run the \acrshort{wdias} as per the required level of load on the system. We used a set of physical nodes, as mentioned in \cref{tab:aws_eks_nodes}, to set up the \acrshort{k8s} for the performance testing with a peak of 300 \acrshort{rps}.

@@

The \acrshort{wdias} uses Helm \cite{CNCFHelmDocumentations} which is a package manager for \acrshort{k8s}. Each microservice within the system deploys and maintains as a Helm chart and the Helm charts \cite{KarunarathneHelmDeployments} for each microservice available within the codebase. For the databases, we used the official helm charts. Using Helm, we can configure resources, the number of replicas needed, deploy new changes, and manage credentials, storage, and proxy settings that are needed for each microservice.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.75\textwidth]{results/work_load/eks_node_setup.pdf}
    \caption{\acrfull{eks} node setup.}
    \label{fi:eks_node_setup}
\end{figure}

### 2020-06-10 results/sec_3-observations.tex
Fixed: Bib IEEE style

\cref{fi:test_obs_all_15m_throughtput} shows the total server's transaction throughput against the number of active threads.
The formula for total server transaction throughput \cite{JMeterPluginsTransactionPlugin} is;
\[
    \displaystyle \frac{<active \quad threads> \times \quad 1 \quad second}{<1 \quad thread \quad response \quad time>}
\]
It shows the statistical maximum possible number of transactions based on the number of users accessing the application.
By combining the \cref{fi:test_obs_all_15m_latency}, this graph shows that the throughput of the system gets increased without much change in the latency, thus it proves the scalability of the \acrshort{wdias}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Load Testing with 15-min Resolution Data with Auto Pod Scaling}
\label{subse:obs_test_plan_all_auto_15min}

Here we did the performance test plan with 15-minute resolution data, which is similar to the above section. However, during the test plan, we enabled the K8s auto-scaling only for higher resource utilized microservices, as explained in \cref{subse:test_plan_metrics}. While performing the above test plans, we noticed the import-ascii-grid-upload microservice is using lots of CPU, and the adapter-grid microservice is using lots of memory. Before starting the test plan, we configured auto-scaling for the import-ascii-grid-upload microservices. However, the adapter-grid microservice is a consistent service for storing netCDF files. If we want to enable the auto-scaling for the service, all microservice instances of adapter-grid need to share data via shared storage. Since \acrshort{eks} does not support multiple reads and writes support volumes \cite{LinuxFoundationPersistentKubernetes}, we are unable to enable auto-scaling during the test plan. However, the test plan performed approximately \num{311e3} of almost similar sample requests during the above sections.

@@

\cref{fi:obs_all_auto_15m_import_export_res} shows the CPU usage and memory usage for import timeseries modules and export timeseries modules with 1-minute resolution. We show the CPU usage with milli CPUs \cite{LinuxFoundationManagingKubernetes} (1 CPU = 1000m CPUs) and the memory usage shown with Megabytes (Mi) \cite{LinuxFoundationManagingKubernetes} in the graphs. Noticeably, the import-ascii-grid-upload microservice used around 10 CPUs at the peak time while using 3.6 Gigabytes (Gb) of memory. Another important fact is, after the test cases finished, the \acrshort{wdias} cooled down the system via K8s auto-scaling and released the resources. Thus, we can see the elasticity of the \acrshort{wdias} according to the workload.

>>>>

\cref{fi:test_obs_all_15m_throughtput} shows the total server's transaction throughput against the number of active threads.
The formula for total server transaction throughput \cite{ApacheSoftwareFoundationJMeter:Plugin} is;
\[
    \displaystyle \frac{<active \quad threads> \times \quad 1 \quad second}{<1 \quad thread \quad response \quad time>}
\]
It shows the statistical maximum possible number of transactions based on the number of users accessing the application.
By combining the \cref{fi:test_obs_all_15m_latency}, this graph shows that the throughput of the system gets increased without much change in the latency, thus it proves the scalability of the \acrshort{wdias}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Load Testing with 15-minute Resolution Data with Auto Pod Scaling}
\label{subse:obs_test_plan_all_auto_15min}

Here we did the performance test plan with 15-minute resolution data, which is similar to the above section. However, during the test plan, we enabled the K8s auto-scaling only for higher resource utilized microservices, as explained in \cref{subse:test_plan_metrics}. While performing the above test plans, we noticed the import-ascii-grid-upload microservice is using lots of CPU, and the adapter-grid microservice is using lots of memory. Before starting the test plan, we configured auto-scaling for the import-ascii-grid-upload microservices. However, the adapter-grid microservice is a consistent service for storing netCDF files. If we want to enable the auto-scaling for the service, all microservice instances of adapter-grid need to share data via shared storage. Since \acrshort{eks} does not support multiple reads and writes support volumes \cite{LinuxFoundationKubernetesVolumes}, we are unable to enable auto-scaling during the test plan. However, the test plan performed approximately \num{311e3} of almost similar sample requests during the above sections.

@@

\cref{fi:obs_all_auto_15m_import_export_res} shows the CPU usage and memory usage for import timeseries modules and export timeseries modules with 1-minute resolution. We show the CPU usage with milli CPUs \cite{LinuxFoundationKubernetes:Containers} (1 CPU = 1000m CPUs) and the memory usage shown with Megabytes (Mi) \cite{LinuxFoundationKubernetes:Containers} in the graphs. Noticeably, the import-ascii-grid-upload microservice used around 10 CPUs at the peak time while using 3.6 Gigabytes (Gb) of memory. Another important fact is, after the test cases finished, the \acrshort{wdias} cooled down the system via K8s auto-scaling and released the resources. Thus, we can see the elasticity of the \acrshort{wdias} according to the workload.
